Thesis Title

### 2022-12-29 chapters/chapter_5.tex
finish hAMRonization paper, fix names formatting on papers
update LMAS DOI

This chapter is a reproduction of the following manuscript accepted for publication in GigaScience:

C. I. Mendes, P. Vila-Cerqueira, Y. Motro, J. Moran-Gilad, J. A. Carriço, M. Ramirez. LMAS: Evaluating metagenomic short de novo assembly methods through defined communities

@@

Catarina I Mendes$^1,*$, 
P Vila-Cerqueira$^1*$,
Y Motro$^2$,
J. Moran-Gilad$^2$,
João A Carriço$^1$
Mário Ramirez$^1$,

>>>>

This chapter is a reproduction of the following manuscript:

C. I. Mendes, P. Vila-Cerqueira, Y. Motro, J. Moran-Gilad, J. A. Carriço, M. Ramirez. LMAS: Evaluating metagenomic short de novo assembly methods through defined communities. GigaScience, Volume 12, 2023, giac122, \url{https://doi.org/10.1093/gigascience/giac122}

@@

Catarina I. Mendes$^1,*$, 
Pedro Vila-Cerqueira$^1*$,
Yair Motro$^2$,
Jacob Moran-Gilad$^2$,
João A. Carriço$^1$
Mário Ramirez$^1$,
